Parameter Estimation for the CES Model

### 2013-07-23 CES.Rnw
Added a comma.
collect data into data frame

<<eval=TRUE>>=
nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
  data <- loadData(countryAbbrev=countryAbbrev)
  data <- replaceColName(data, energyType, "iEToFit")
  if (nest == "(kl)e"){
    xNames <- c("iCapStk", "iLabor", "iEToFit")
  } else if (nest == "(le)k"){
    xNames <- c("iLabor", "iEToFit", "iCapStk")
  } else if (nest == "(ek)l"){
    xNames <- c("iEToFit", "iCapStk", "iLabor")
  } else {
    stop(paste("Unknown nesting option", nest, "in fitCES."))
  }
  model <- cesEst(data=data, 
                  yName="iGDP", 
                  xNames=xNames, 
                  tName="iYear",
                  method=method)
}

# Make all the models
kleModels <- lapply(countryAbbrevs, fitCES, nest="(kl)e")
lekModels <- lapply(countryAbbrevs, fitCES, nest="(le)k")
eklModels <- lapply(countryAbbrevs, fitCES, nest="(ek)l")

modelMatrix <- cbind(kleModels, lekModels, eklModels)
colnames(modelTable) <- nestingOptions

# Now, extract coefficients from each model in the matrix
# to make data.frames of coefficients. Each data.frame has 
# countries in rows and nesting options in columns 
# (same structure) as modelMatrix

>>>>

<<eval=TRUE>>=
require(plyr)
nestingOptions <- c(kle="(kl)e", lek="(le)k", ekl="(ek)l")
fitCES <- function(countryAbbrev, nest, energyType="Q", method="L-BFGS-B"){
  data <- loadData(countryAbbrev=countryAbbrev)
  data <- replaceColName(data, energyType, "iEToFit")
  if (nest == "(kl)e"){
    xNames <- c("iCapStk", "iLabor", "iEToFit")
  } else if (nest == "(le)k"){
    xNames <- c("iLabor", "iEToFit", "iCapStk")
  } else if (nest == "(ek)l"){
    xNames <- c("iEToFit", "iCapStk", "iLabor")
  } else {
    stop(paste("Unknown nesting option", nest, "in fitCES."))
  }
  model <- cesEst(data=data, 
                  yName="iGDP", 
                  xNames=xNames, 
                  tName="iYear",
                  method=method)
  return(c(coef( model ), c(country=countryAbbrev, nest=nest)) )
}

# Make all the models
kleModels <- ldply(countryAbbrevs, fitCES, nest="(kl)e")
lekModels <- ldply(countryAbbrevs, fitCES, nest="(le)k")
eklModels <- ldply(countryAbbrevs, fitCES, nest="(ek)l")
allModels <- rbind(kleModels, lekModels, eklModels)
#modelMatrix <- cbind(kleModels, lekModels, eklModels)
#colnames(modelTable) <- nestingOptions

# Now, extract coefficients from each model in the matrix
# to make data.frames of coefficients. Each data.frame has 
# countries in rows and nesting options in columns, 
# (same structure) as modelMatrix
